Tight Bounds for Dynamic Balanced Graph Partitioning

### 2020-05-09 paper/disc20clustering.tex
Intro to LB

We provide a lower bound $\Omega(k\cdot \ell)$ for the competitive ratio of any deterministic online algorithm for the learning problem.
Later we elaborate on how to efficiently transform it to a lower bound for the general partitioning problem.
The lower bound requires $k\geq 3$.
For $k=2$, the learning problem is trivial: immediate collocation of a communicating pair is $1$-competitive.
(A partitioning problem for $k=2$ is non-trivial, a lower bound of $3$ is known \cite{repartition-disc}, and we provide a~$6$-competitive algorithm (see Section~\ref{sec:k2}).)

>>>>

We provide a lower bound $\Omega(k\cdot \ell)$ for the competitive ratio of any deterministic online algorithm for the learning problem.
Later we elaborate on how to efficiently transform it to a lower bound for the general partitioning problem.
The lower bound requires $k\geq 3$.
For $k=2$, the learning problem is trivial: immediate collocation of a communicating pair is $1$-competitive.
(A partitioning problem for $k=2$ is non-trivial, a lower bound of $3$ is known \cite{repartition-disc}, and we provide a~$6$-competitive algorithm, see Section~\ref{sec:k2}.)
